Another paper with lots of text and fancy pictures

### 2023-12-01 paper.tex
Replace an ellipsoid with a dumbbell

To test $F_{sss}$ function we use a recently developed approach which computes
that function for sets defined by inequation $f(x) \le T$, $x \in \mathbb{R}^3$
with help of automatic differentiation \cite{postnicov20232}. We choose $f$
\begin{equation}
  f(x, y, z) = (|2x|^{\frac{3}{2}} + |y|^{\frac{3}{2}} + |z|^{\frac{3}{2}})^{\frac{2}{3}}
\end{equation}
so inequation $f(x, y, z) \le T$ gives us an ellipsoid-like object
(\cref{fig:sss-ellipsoid}).

The test was performed by evaluating the inequation with the parameter $T = 0.4$
in a cube $[-1, 1]^3$ and comparing $F_{sss}$ calculated by our algorithm with
precise values. Pointwise relative error of $F_{sss}$ is on
\cref{fig:sss-ellipsoid-error}. Maximal relative error in the area bound by
inequations $x > 0.1$, $y > 0.1$ and $f(x, y) < 0.78$ is about 10\%.
\begin{figure*}[tp]
  \centering
  \subfigure[The ellipsoid-like object used in testing of $F_{sss}$ computation]{
    \includegraphics[width=0.45\linewidth]{images/ellipsoid.png}
    \label{fig:sss-ellipsoid}}
  \hfill
  \subfigure[Relative error of computation]{
    \includegraphics[width=0.45\linewidth]{images/ellipsoid-sss-diff.png}
    \label{fig:sss-ellipsoid-error}}
  \vskip\baselineskip
  \subfigure[$F_{sss}$: precise]{
    \includegraphics[width=0.45\linewidth]{images/ellipsoid-sss.png}}
  \hfill
  \subfigure[$F_{sss}$: calculated with our approach]{
    \includegraphics[width=0.45\linewidth]{images/ellipsoid-sss-julia.png}}
  \caption[]{A comparison of $F_{sss}$ function calculated using our approach
    with its precise values.}
  \label{fig:sss-verification}
\end{figure*}

>>>>

To test $F_{sss}$ function we use a recently developed approach which computes
that function for sets defined by inequation $f(x) \le T$, $x \in \mathbb{R}^3$
with help of automatic differentiation \cite{postnicov20232}. We choose $f$ as
\begin{equation}
  f(x, y, z) = y^2 + z^2 - a x^2 (b^2 - x^2)
\end{equation}
and parameters $a = 10$, $b = 0.45$, $T = 10^{-2}$, so inequation
$f(x, y, z) \le T$ gives us a dumbbell-like object (\cref{fig:sss-dumbbell}).

The test was performed by firstly evaluating the inequation in a cube
$[-1, 1]^3$ and obtaining precise values of $F_{sss}$ and secondly computing
$F_{sss}$ with our algorithm, giving a discretized $400 \times 400 \times 400$
pixels wide image as the input. Pointwise relative error of $F_{sss}$ is on
\cref{fig:sss-dumbbell-error}. Maximal relative error in the area distanced
farther than 0.1 (20 pixels) from curves of discontinuity (look at
\cref{fig:sss-dumbbell-precise}) is no more than 20\%.
\begin{figure*}[tp]
  \centering
  \subfigure[The dumbbell-like object used in testing of $F_{sss}$ computation]{
    \includegraphics[width=0.45\linewidth]{images/dumbbell.png}
    \label{fig:sss-dumbbell}}
  \hfill
  \subfigure[Relative error of computation]{
    \includegraphics[width=0.45\linewidth]{images/dumbbell-sss-err.png}
    \label{fig:sss-dumbbell-error}}
  \vskip\baselineskip
  \subfigure[$F_{sss}$: precise. The correlation function is undefined (has type
    II discontinuity) at curves A, B and C.]{
    \includegraphics[width=0.45\linewidth]{images/dumbbell-sss-precise.png}
    \label{fig:sss-dumbbell-precise}}
  \hfill
  \subfigure[$F_{sss}$: calculated with our approach]{
    \includegraphics[width=0.45\linewidth]{images/dumbbell-sss-julia.png}}
  \caption[]{A comparison of $F_{sss}$ function calculated using our approach
    with its precise values.}
  \label{fig:sss-verification}
\end{figure*}
